### 2014-09-05 pontoControle1/editaveis/proposta.tex

\chapter*[Proposta]{Proposta}
\addcontentsline{toc}{chapter}{Proposta}