### 2014-09-05 pontoControle1/editaveis/resultados.tex

\chapter*[Resultados]{Resultados}
\addcontentsline{toc}{chapter}{Resultados}