### 2014-09-05 pontoControle1/editaveis/financeiro.tex
Change chapter* to chapter

\chapter[Financeiro]{Financeiro}
\addcontentsline{toc}{chapter}{Financeiro}