### 2014-09-14 editaveis/figura.tex

  
  \def\firstcircle{(0:2.75cm)  circle (2.85cm)}
  \def\secondcircle{(90:2.75cm) circle (2.85cm)}
  \def\thirdcircle{(180:2.75cm) circle (2.85cm)}
  \def\fourdcircle{(270:2.75cm) circle (2.85cm)}

\tikzstyle{sensor}=[draw, fill=blue!20, text width=5em, 
    text centered, minimum height=2.5em,drop shadow]
\tikzstyle{wa} = [sensor, text width=10em, fill=red!20, 
    minimum height=6em, rounded corners, drop shadow]

  \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=5cm,
  thick,scale=0.8]

    % The last trick is to cheat and use transparency
    \begin{scope}[shift={(3cm,3cm)}, fill opacity=0.5]
        \fill[red] \firstcircle;
        \fill[green] \secondcircle;
        \fill[blue] \thirdcircle;
        \fill[yellow] \fourdcircle;

        \draw \firstcircle node[right] (a) {$Software$}
        	[clockwise from=30,level distance=140,sibling angle=43]
			child { node[concept,text width=3cm,align=center] {Gerenciamento} }
			child {node[concept,text width=3cm,align=center] {Modelagem} }
			child { node[concept,text width=3cm,align=center] {Óculos de Realidade Virtual} }
        ;
        \draw \secondcircle node [above] (b) {$Eletrônica$}
        [clockwise from=90,level distance=170,sibling angle=30]
        	child { node[concept,text width=3cm,align=center] {Sensores} }
        ;
        \draw \thirdcircle node [left] (c) {$Energia$}
        [clockwise from=240,level distance=140,sibling angle=45]
        	child { node[concept,text width=3cm,align=center] {Armazenamento de Energia} }
        	child { node[concept,text width=3cm,align=center] {Conversão Electromecânica} }
        	child { node[concept,text width=3cm,align=center] {Eficiência Energética} }
        	child { node[concept,text width=3cm,align=center] {Distribuição} }
        ;
        \draw \fourdcircle node [below] (d) {$Automotiva$}
        [clockwise from=295,level distance=170,sibling angle=40]
        	child { node[concept,text width=3cm,align=center] {Ergonomia} }
        	child { node[concept,text width=3cm,align=center] {Analise Estrutural} }
        ;
    \end{scope}

\end{tikzpicture}