### 2014-10-08 editaveis/anexos.tex
Fix Zebra problem

\begin{anexosenv}

\partanexos

\chapter{Códigos Fontes}

%\lstinputlisting[language=Python,caption={main.py}]{../startx-src/device/scripts/main.py}

%\chapter{Segundo Anexo}

%Texto do segundo anexo.

\end{anexosenv}