### 2014-10-22 editaveis/automotiva_planejamento.tex
Update automotiva_planejamento.tex

Estrutura baseada....na figura \ref{fig:awesome_image}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{figuras/perfil_t.png}
    \caption{Estrutura}
    \label{fig:awesome_image}
\end{figure}