### 2014-12-02 editaveis/eletronica_software.tex

% Comentar a integração entre eletronica e software