### 2014-12-02 editaveis/energia_automotiva.tex

% Comentar a integração entre energia e automotiva